Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-30 paper.tex
revise start of introduction

\section{Introduction}
\label{sec:introduction}
Surfaces with gradient in the refractive index (GRIN) are of
importance not only due to the possibility of being able to
engineer/tune the propagation of light within the structure’s
surface for applications such as flat lenses, but also for several
interesting biological applications where the continual topographical
variation is being exploited \cite{pierscionek2012gradient}. As an example,
roughness dependent  response of the cells has been tested on such
materials for applications in medical implants \cite{bai2020bioinspired}.
 Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew.
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman,
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas.
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS
on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.
Among the electrochemical methods, compositional and doping density changes
in the conducting polymer have been used to produce the gradients using Indium tin
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach with an additional advantage of being compatible
with VLSI devices and integrable with microelectronics, for the fabrication
of refractive index (pore size) gradient has been the development of asymmetric
electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.

>>>>

\section{Introduction}
\label{sec:introduction}
Surfaces with a gradient in the refractive index (GRIN) are of
importance as they allow the engineering and tuning of the optical
phase along their surface, yielding applications such as flat
lenses. Furtheremore, there are important biological applications
which combine topographical features with index of refraction
gradients \cite{pierscionek2012gradient}. Preparation of structures
with gradients in other properties have also shown their
usefulness. \notaL{I believe the examples below are unrelated to GRIN,
  thats why I added this remark.} As an example, the
roughness dependent  response of cells has been tested on
materials used applications in medical implants
\cite{bai2020bioinspired}.
Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition
gradients of CdS layers
on gold electrodes have been obtained made by Shannon’s
group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
  why should we name him?}
Among electrochemical methods, compositional and doping density changes
in  conducting polymers have been used to produce gradients using Indium Tin
Oxide electrodes \cite{inagi2010bipolar}
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach for the fabrication
of gradient materials has been the use  of asymmetrical
electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
This technique has the additional advantage of being compatible
with VLSI devices and integrable with microelectronics.
